---
title: "R Notebook"
output: html_notebook
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Generating the clinical-radiomics model

# model 1 (BMUS radiomics model) is BMUS Rad-score combined with composition, margin, and echogenic foci
```{r}
library("rms")
library("ggplot2")
library("pROC")
df_clinical_radiomics <- read.csv(
  file="./dataset/combind model/sample_Clinical_Radiomics.csv", 
  header=T, sep=',', stringsAsFactors = F)
model1 <- rms::lrm(
  formula="Label ~ Signature_BMUS + composition + margin + echogenic_foci", 
  x=T,y=T, data = df_train_data)
summary(model1)
save(model1, file = "./dataset/combind model/result/model1.RData")
nomo_model1 <- rms::nomogram(
  model1,
  fun=plogis,
  fun.at=c(.001, .01, seq(.1,.9, by=.2), .99, .999),
  lp=F,
  maxscale=100,
  funlabel="Risk")
plot(nomo_model1, xfrac = 0.6)

predictValue = predict(model1, df_clinical_radiomics)
roc_obj <- pROC::roc(
    response=df_clinical_radiomics$Label, 
    predictor=plogis(predict(model1, df_clinical_radiomics)))
best_threshold <- pROC::coords(roc_obj, "best", ret=c("threshold"), drop = T, transpose = TRUE)[1]
print(sprintf("Cut-off value is %f.", best_threshold))
plot(roc_feature_obj, main = "Model 1", lwd=3) 
```

# model 2 (BMUS+SMI radiomics model) is BMUS-SMI Rad-score combined with composition, margin, echogenic foci, and SMI vascularity type
```{r}
library("rms")
library("ggplot2")
library("pROC")
df_clinical_radiomics <- read.csv(
  file="./dataset/combind model/sample_Clinical_Radiomics.csv", 
  header=T, sep=',', stringsAsFactors = F)
model2 <- rms::lrm(
  formula="Label ~ Signature_BMUS_SMI + margin + SMI_vascular_type", 
  x=T,y=T, data = df_train_data)
summary(model2)
save(model2, file = "./dataset/combind model/result/model2.RData")
nomo_model2 <- rms::nomogram(
  model2,
  fun=plogis,
  fun.at=c(.001, .01, seq(.1,.9, by=.2), .99, .999),
  lp=F,
  maxscale=100,
  funlabel="Risk")
plot(nomo_model2, xfrac = 0.6)

predictValue = predict(model2, df_clinical_radiomics)
roc_obj <- pROC::roc(
    response=df_clinical_radiomics$Label, 
    predictor=plogis(predict(model2, df_clinical_radiomics)))
best_threshold <- pROC::coords(roc_obj, "best", ret=c("threshold"), drop = T, transpose = TRUE)[1]
print(sprintf("Cut-off value is %f.", best_threshold))
plot(roc_feature_obj, main = "Model 2", lwd=3) 
```

# model 3 (BMUS+CEUS radiomics model) is BMUS+CEUS Rad-score combined with composition, margin, echogenic foci, and enhancement direction
```{r}
library("rms")
library("ggplot2")
library("pROC")
df_clinical_radiomics <- read.csv(
  file="./dataset/combind model/sample_Clinical_Radiomics.csv", 
  header=T, sep=',', stringsAsFactors = F)
model3 <- rms::lrm(
  formula="Label ~ Signature_BMUS_CEUS + margin + echogenic_foci + Enhancement_direction2", 
  x=T,y=T, data = df_train_data)
summary(model3)
save(model3, file = "./dataset/combind model/result/model3.RData")
nomo_model3 <- rms::nomogram(
  model3,
  fun=plogis,
  fun.at=c(.001, .01, seq(.1,.9, by=.2), .99, .999),
  lp=F,
  maxscale=100,
  funlabel="Risk")
plot(nomo_model3, xfrac = 0.6)

predictValue = predict(model3, df_clinical_radiomics)
roc_obj <- pROC::roc(
    response=df_clinical_radiomics$Label, 
    predictor=plogis(predict(model3, df_clinical_radiomics)))
best_threshold <- pROC::coords(roc_obj, "best", ret=c("threshold"), drop = T, transpose = TRUE)[1]
print(sprintf("Cut-off value is %f.", best_threshold))
plot(roc_feature_obj, main = "Model 3", lwd=3) 
```

# model 4 (BMUS+SMI+CEUS radiomics model) is BMUS+SMI+CEUS Rad-score combined with margin, echogenic foci, SMI vascularity type, and enhancement direction. 
```{r}
library("rms")
library("ggplot2")
library("pROC")
df_clinical_radiomics <- read.csv(
  file="./dataset/combind model/sample_Clinical_Radiomics.csv", 
  header=T, sep=',', stringsAsFactors = F)
model4 <- rms::lrm(
  formula="Label ~ Signature_ALL + echogenic_foci + Enhancement_direction2 + 
    SMI_vascular_type", 
  x=T,y=T, data = df_train_data)
summary(model4)
save(model4, file = "./dataset/combind model/result/model4.RData")
nomo_model4 <- rms::nomogram(
  model4,
  fun=plogis,
  fun.at=c(.001, .01, seq(.1,.9, by=.2), .99, .999),
  lp=F,
  maxscale=100,
  funlabel="Risk")
plot(nomo_model4, xfrac = 0.6)

predictValue = predict(model4, df_clinical_radiomics)
roc_obj <- pROC::roc(
    response=df_clinical_radiomics$Label, 
    predictor=plogis(predict(model4, df_clinical_radiomics)))
best_threshold <- pROC::coords(roc_obj, "best", ret=c("threshold"), drop = T, transpose = TRUE)[1]
print(sprintf("Cut-off value is %f.", best_threshold))
plot(roc_feature_obj, main = "Model 4", lwd=3) 
```
